A Tutorial on Tailored Simulation-Based Sample Size Planning for Experimental Designs with Generalized Linear Mixed Models

### 2024-04-10 docs/manuscript.Rmd
new pdf for team review; update packages, update results file, update bib file

@@

- Lakens ebook evtl. Andy Field für die Basics?
- R for data science, Bruine article, faux documentation für die R skills
- kumle power tutorial und irgendwelche paper (am besten aus AMPPS) zu GLMMs
- what is your estimand? paper für das estimand topic

>>>>

TODO: fertig ausformulieren

@@

- Lakens ebook [@lakensImprovingYourStatistical2022] evtl. Andy Field für die Basics?
- R for data science [@wickhamDataScienceImport2023], Bruine article [@debruineUnderstandingMixedEffectsModels2021], faux documentation [@R-faux] für die R skills
- kumle power tutorial [@kumleEstimatingPowerGeneralized2021] und irgendwelche paper (am besten aus AMPPS) zu GLMMs
- what is your estimand? paper [@lundbergWhatYourEstimand2021] für das estimand topic
